\renewcommand{\baselinestretch}{\yuanbeishu}\normalsize%
\zihao{5}                                              %
% \addcontentsline{toc}{section}{参考文献}
\begin{thebibliography}{99}                            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \bibitem{Amemiya84}
% Amemiya, T. (1984). Tobit models: A survey. {\it Journal of Econometrics}, {\bf 24(1-2)}, 3-61.

% \bibitem{Austin00}
% Austin, P.C., Escobar, M. and Kopec, J. A. (2000). The use of the Tobit model for analyzing measures of health status. {\it Quality of Life Research}, {\bf 9(8)}, 901-910.

% \bibitem{Authority10}
% Authority, E. (2010). Management of left-censored data in dietary exposure assessment of chemical substances. {\it Efsa Journal}, {\bf 8(3)}, 1557.

% \bibitem{Chu05}
% Chu, H. and Nie, L. (2005). A note on comparing exposure data to a regulatory limit in the presence of unexposed and a limit of detection. {\it Biometrical Journal}, {\bf 47(6)}, 880-887.

% \bibitem{Cohen59}
% Cohen, A. C. (1959). Simplified estimators for the normal distribution when samples are singly censored or truncated. {\it Technometrics}, {\bf 1(3)}, 217-237.

% \bibitem{Dagne13}
% Dagne, G.A. and Huang, Y. (2013). Bayesian semiparametric mixture Tobit models with left censoring, skewness and covariate measurement errors. {\it Statistics in Medicine}, {\bf 32(22)}, 3881-3898.

% \bibitem{Dinse14}
% Dinse, G.E., et al. (2014). Accommodating measurements below a limit of detection: a novel application of Cox regression. {\it American Journal of Epidemiology}, {\bf 179(8)}, 1018-1024.

% \bibitem{Farewell82}
% Farewell, V.T. (1982). The use of mixture models for the analysis of survival data with long-term survivors. {\it Biometrics}, {\bf 38(4)}, 1041-1046.

% \bibitem{Ferrero17}
% Ferrero, A., Esplugues, A., Estarlich, M., et al. (2017). Infants' indoor and outdoor residential exposure to benzene and respiratory health in a Spanish cohort. {\it Environmental Pollution}, {\bf 222}, 486-494.

% \bibitem{Frone94}
% Frone, M.R., Cooper, M.L. and Russell, M. (1994). Stressful life events, gender and substance use: An application of tobit regression. {\it Psychology of Addictive Behaviors}, {\bf 8(2)}, 59-69.

% \bibitem{Alan85}
% Gleit, A. (1985). Estimation for small normal data sets with detection limits. {\it Environmental Science and Technology}, {\bf 19(12)}, 1201-1206.

% \bibitem{Halsey85}
% Halsey, N.A., Boulos, R., Mode, F., et al. (1985). Response to measles vaccine in Haitian infants 6 to 12 months old: influence of maternal antibodies, malnutrition and concurrent illnesses. {\it New England Journal of Medicine}, {\bf 313(9)}, 544-549.

% \bibitem{He20}
% He, H., Mi, X. and Tang, W. (2020). Statistical issues on analysis of censored data due to detection limit. {\it International Journal of Statistics and Probability}, {\bf 9(4)}, 49-61.

% \bibitem{HeH20}
% He H, Tang W, Kelly T, Li S and He J. (2020). Statistical tests for latent class in censored data due to detection limit. {\it Statistical Methods in Medical Research}, {\bf 29(8)}, 2179-2197.

% \bibitem{Hornung90}
% Hornung, R.W. and Reed, L.D. (1990). Estimation of average concentration in the presence of nondetectable values. {\it Applied Occupational and Environmental Hygiene}, {\bf 5(1)}, 46-51.

% \bibitem{Hughes99}
% Hughes, J.P. (1999). Mixed effects models with censored data with application to HIV RNA levels. {\it Biometrics}, {\bf 55(2)}, 625-629.

% \bibitem{Jamjoum02}
% Jamjoum, L.S., Bielak, L.F., et al. (2002). Relationship of blood pressure measures with coronary artery calcification. {\it Medical Science Monitor}, {\bf 8(12)}, CR775-CR781.

% \bibitem{Kakourou18}
% Kakourou, A., Vach, W. and Mertens, B. (2018). Adapting censored regression methods to adjust for the limit of detection in the calibration of diagnostic rules for clinical mass spectrometry proteomic data. {\it Statistical Methods in Medical Research}, {\bf 27(9)}, 2742-2755.

% \bibitem{Kim18}
% Kim S, Chang Y, Sung E, et al. (2018). Association between sonographically diagnosed nephrolithiasis and subclinical coronary artery calcification
% in adults. {\it American Journal of Kidney Diseases}, {\bf 71(1)}, 35-41.

% \bibitem{Lankester13}
% Lankester, J., Patel, C., Cullen, M. R., Ley, C. and Parsonnet, J. (2013). Urinary triclosan is associated with elevated body mass index in NHANES. {\it PloS One}, {\bf 8(11)}, e80057.

% \bibitem{Li15}
% Li, S., Zhao, J., Wang, G., et al. (2015). Urinary triclosan concentrations are inversely associated with body mass index and waist circumference in the US general population: experience in NHANES 2003-2010. {\it International Journal of Hygiene and Environmental health}, {\bf 218(4)}, 401-406.

% \bibitem{Lubin04}
% Lubin, J.H., Colt, J. S., et al. (2004). Epidemiologic evaluation of measurement data in the presence of detection limits. {\it Environmental Health Perspectives}, {\bf 112(17)}, 1691-1696.

% \bibitem{Maddala93}
% Maddala, G.S. (1993). 7 Estimation of limited dependent variable models under rational expectations. {\it Handbook of Statistics}, {\bf 11(1)}, 175-194.

% \bibitem{McDonald80}
% McDonald, J. F. and Moffitt, R. A. (1980). The uses of Tobit analysis. {\it The Review of Economics and Statistics}, {\bf 62(2)}, 318-321.

% \bibitem{Moulton95}
% Moulton, L.H. and Halsey, N.A. (1995). A mixture model with detection limits for regression analyses of antibody response to vaccine. {\it Biometrics}, {\bf 51(4)}, 1570-1578.

% \bibitem{Nassan17}
% Nassan, Feiby L., Coull, B.A., et al. (2017). Personal care product use in men and urinary concentrations of select phthalate
% metabolites and parabens: results from the Environment and Reproductive Health (EARTH) study. {\it Environmental Health Perspectives}, {\bf 125(8)}, 087012-1-087012-10.

% \bibitem{Newman89}
% Newman, M. C., Dixon, P. M., Looney, B. B. and Pinder III, J. E. (1989). Estimating mean and variance for environmental samples with below detection limit observations 1. {\it JAWRA Journal of the American Water Resources Association}, {\bf 25(4)}, 905-916.

% \bibitem{Olsen78}
% Olsen, R.J. (1978). Note on the uniqueness of the maximum likelihood estimator for the Tobit model. {\it Econometrica}, {\bf 46(5)}, 1211-1215.

% \bibitem{Ostergren17}
% Ostergren, P.B., Kistorp, C., Fode, M., Henderson, J., Bennedbaek, F. N., Faber, J. and Sonksen, J. (2017). Luteinizing hormone-releasing hormone agonists are superior to subcapsular orchiectomy in lowering testosterone levels of men with prostate cancer: results from a randomized clinical trial. {\it The Journal of Urology}, {\bf 197(6)}, 1441-1447.

% \bibitem{Park17}
% Park, M. and Lee, D. (2017). Analysis of severe injury accident rates on interstate highways using a random parameter tobit model. {\it Mathematical Problems in Engineering}, {\bf 2017}, 1-6.

% \bibitem{TR13}
% R Core Team. (2019). R: A Language and Environment for Statistical Computing. R for Statistical Computing, Vienna. https://www.R-Project.org


% \bibitem{Reilly04}
% Reilly, M.P., Wolfe, M. L., et al. (2004). Coronary artery calcification and cardiovascular risk factors: impact of the analytic approach. {\it Atherosclerosis}, {\bf 173(1)}, 69-78.


% \bibitem{Reisetter17}
% Reisetter, A.C., et al. (2017). Mixture model normalization for non-targeted gas chromatography/mass spectrometry metabolomics data. {\it BMC Bioinformatics}, {\bf 18(1)}, 1-17.

% \bibitem{Setty17}
% Setty, K. E., Kayser, G. L., et al. (2017). Water quality, compliance and health outcomes among utilities implementing Water Safety Plans in France and Spain - ScienceDirect. {\it International Journal of Hygiene and Environmental Health}, {\bf 220(3)}, 513-530.

% \bibitem{Slymen94}
% Slymen, D.J., de Peyster, A. and Donohoe, R.R. (1994). Hypothesis testing with valBues below detection limit in environmental studies. {\it Environmental Science and Technology}, {\bf 28(5)}, 898-902.

% \bibitem{Taylor01}
% Taylor, D. J., Kupper, L. L., Rappaport, S. M. and Lyles, R. H. (2001). A mixture model for occupational exposure mean testing with a limit of detection. {\it Biometrics}, {\bf 57(3)}, 681-688.

% \bibitem{Tobin58}
% Tobin, J. (1958). Estimation of relationships for limited dependent variables. {\it Econometrica}, {\bf 26(1)}, 24-36.

% \bibitem{Wang17}
% Wang, W. and Griswold, M. E. (2017). Natural interpretations in Tobit regression models using marginal estimation methods. {\it Statistical Methods in Medical Research}, {\bf 26(6)}, 2622-2632.


\bibitem{CHben92}
本间则行, 刘倩. (1992). 急性肾功能衰竭治疗的新进展. {\it 日本医学介绍}, {\bf 13(5)}, 213-215.

\bibitem{CHcheng18}
陈伟伟, 高润霖, 刘力生等. (2018).《中国心血管病报告 2017》概要. {\it 中国循环杂志}, {\bf 33(1)}, 1-8.

\bibitem{CHhuang20}
黄平秀. (2020). 急性肾衰竭患者的临床护理新进展. {\it 中国城乡企业卫生}, {\bf 35(3)}, 68-70.

\bibitem{CHjie15}
解修花. (2016). 终末期肾脏病患者自我感受负担及其影响因素的调查分析. {\it 实用临床医学}, {\bf 17(12)}, 91-94.

\bibitem{CHli18}
李艳艳, 单岩, 刘赛赛, 常天颖, 杜理平, 蒋婷婷. (2018). 终末期肾脏病患者疾病感知的研究进展. {\it 中华护理教育}, {\bf 15(8)}, 584-588.

\bibitem{CHsong19}
宋波, 宋同峰. (2019). 慢性肾病辅助诊断系统的设计与实现. {\it 计算机测量与控制}, {\bf 27(10)}, 50-54.

\bibitem{CHwang18}
王骞. (2018). IgA肾病的中西医治疗进展. {\it 现代中西医结合杂志}, {\bf27(8)}, 898-902.

\bibitem{CHyang08}
阳晓. (2008). 慢性肾脏病进展的危险因素及延缓策略. {\it 中国实用内科杂志}, {\bf 28(1)}, 79-80.

\bibitem{CHzhang10}
张晓光, 汪年松. (2007). 慢性肾脏病危险因素的研究进展. {\it 实用医学杂志}, {\bf 23(23)}, 3641-3643.

\bibitem{CHzhao17}
赵敏, 彭海平. (2017). 刘宝厚教授从血瘀论治慢性肾衰竭经验. {\it 中国老年保健医学}, {\bf 15(3)}, 2-3.

\bibitem{CHzhong09}
中华医学会, 陈香美. (2009). 临床技术操作规范:肾脏病学分册. {\it 人民军医出版社}.

\bibitem{Breiman01}
Breiman, L. (2001). Statistical modeling: the two cultures (with comments and a rejoinder by the author). {\it Statistical Science}, {\bf 16(3)}, 199-215.

\bibitem{Biganzoli98}
Biganzoli, E., Boracchi, P., Mariani, L., and Marubini, E. (1998). Feed forward neural networks for the analysis of censored survival data: a partial logistic regression approach. {\it Statistics in Medicine}, {\bf 17(10)}, 1169-1186.

\bibitem{CDC07}
Centers for Disease Control and Prevention. (2007). Prevalence of chronic kidney disease and associated risk factors - United States, 1999-2004. {\it Morbidity and Mortality Weekly Report}, {\bf 56(8)}, 161-165.

\bibitem{Cox72}
Cox, D.R. (1972). Regression models and life-tables. {\it Journal of the Royal Statistical Society Series B-Statistical Methodology}, {\bf34(2)}, 187-220.

\bibitem{Efron79}
Efron, B. (1979). Bootstrap methods: another look at the jackknife. {\it Annals of Statistics}, {\bf 7(1)}, 1-26.

\bibitem{Faraggi95}
Faraggi, D., and Simon, R. (1995). A neural-network model for survival-data. {\it Statistics in Medicine}, {\bf 14(1)}, 73-82.

\bibitem{Fern16}
Fernandez, T., Rivera, N., and Teh, Y.W. (2016). Gaussian processes for survival analysis. {\it Neural Information Processing Systems}, {\bf 2016}, 5021-5029. 

\bibitem{Goldberger00}
Goldberger, A., Amaral, L., Glass, L., Hausdorff, J., Ivanov, P. C., Mark, R., et al. (2000). PhysioBank, PhysioToolkit, and PhysioNet: Components of a new research resource for complex physiologic signals. {\it Circulation}. {\bf 101(23)}, 215-220.

\bibitem{Graf99}
Graf, E., Schmoor, C., Sauerbrei, W., and Schumacher, M. (1999). Assessment and comparison of prognostic classification schemes for survival data. {\it Statistics in Medicine}, {\bf 18(17)}, 2529-2545.

\bibitem{Groeger93}
Groeger, J.S., Guntupalli, K.K., Strosberg, M., Halpern, N., Raphaely, R.C., Cerra, F., and Kaye, W. (1993). Descriptive analysis of critical care units in the United States: patient characteristics and intensive care unit utilization. {\it Critical Care Medicine}, {\bf 21(2)}, 279-291.

\bibitem{Halpern10}
Halpern, N.A., and Pastores, S.M. (2010). Critical care medicine in the United States 2000-2005: an analysis of bed numbers, occupancy rates, payer mix, and costs. {\it Critical Care Medicine}, {\bf 38(1)}, 65-71.

\bibitem{Harrell82}
Harrell, F.E., Jr, Califf, R.M., Pryor, D.B., Lee, K.L., and Rosati, R.A. (1982). Evaluating the yield of medical tests. {\it JAMA}, {\bf 247(18)}, 2543-2546.

\bibitem{Patrick05}
Heagerty, P., and Zheng, Y. (2004). Survival model predictive accuracy and ROC curves. {\it Biometrics}, {\bf 61(1)}, 92-105

\bibitem{Herzlinger02}
Herzlinger D. (2002). Renal interstitial fibrosis: remembrance of things past. {\it The Journal of Clinical Investigation}, {\bf 110(3)}, 305-306.

\bibitem{Ishwaran08}
Ishwaran, H., Kogalur, U.B., Blackstone, E.H., and Lauer, M.S. (2008). Random survival forests. {\it Annals of Applied Statistics}, {\bf 2(3)}, 841-860.

\bibitem{Jerez05}
Jerez, J.M., Franco, L., Alba, E., Llombart-Cussac, A., Lluch, A., Ribelles, N., Munarriz, B., and Martin, M. (2005). Improvement of breast cancer relapse prediction in high risk intervals using artificial neural networks. {\it Breast Cancer Research and Treatment}, {\bf 94(3)}, 265-272.

% \bibitem{Johnson21}
% Johnson, A., Bulgarelli, L., Pollard, T., Horng, S., Celi, L. A., and Mark, R. (2021). MIMIC-IV (version 1.0). {\it PhysioNet}.

\bibitem{Johnston12}
Johnston, G. (2012). Statistical Models and Methods for Lifetime Data. {\it Wiley}. 

\bibitem{Kamarudin17}
Kamarudin, A.N., Cox, T., and Kolamunnage-Dona, R. (2017). Time-dependent ROC curve analysis in medical research: current methods and applications. {\it BMC Medical Research Methodology}, {\bf 17(1)}, 1-19.

\bibitem{Kaplan58}
Kaplan, E.L., and Meier, P. (1958). Nonparametric Estimation from Incomplete Observations. {\it Journal of the American Statistical Association}, {\it 53(1)}, 457-481.

\bibitem{Katzman18}
Katzman, J.L., Shaham, U., Cloninger, A., Bates, J., Jiang, T., et al. (2018). DeepSurv: personalized treatment recommender system using a Cox proportional hazards deep neural network. {\it BMC Medical Research Methodology}, {\bf 18(1)}, 1-12.

\bibitem{Kvamme19}
Kvamme, H., Borgan, O., and Scheel, I. (2019). Time-to-Event Prediction with Neural Networks and Cox Regression. {\it Journal of Machine Learning Research}, 20(129), 1-30.

\bibitem{Kvamme21}
Kvamme, H., Borgan,.. (2021). Continuous and discrete-time survival prediction with neural networks. {\it Lifetime Data Analysis}, {\bf 27(4)}, 710-736.

\bibitem{Le84}
Le Gall, J.R., Loirat, P., Alperovitch, A., Glaser, P., Granthil, C., Mathieu, D., Mercier, P., Thomas, R., and Villers, D. (1984). A simplified acute physiology score for ICU patients. {\it Critical Care Medicine}, {\bf 12(11)}, 975-977.

\bibitem{Lee18}
Lee, C., Zame, W. R., Yoon, J., and Schaar, M. V. D. (2018). DeepHit: A Deep Learning Approach to Survival Analysis with Competing Risks. {\it AAAI Conference on Artificial Intelligence}, {\bf 32(1)}, 2314-2321. 

\bibitem{Lee93}
Lee, K. H., Hui, K. P., Lim, T. K., Tan, W. C. (1993). Acute physiology and chronic health evaluation (APACHE II) scoring in the Medical Intensive Care Unit, National University Hospital, Singapore. {\it Singapore Medical Journal}, {\bf 34(1)}, 41-44.

\bibitem{Lee06}
Lee, M. L. T., and Whitmore, G. A. (2006). Threshold regression for survival analysis: Modeling event times by a stochastic process reaching a boundary. {\it Statistical Science}, {\bf 21(4)}, 501-513.

\bibitem{Lee10}
Lee, M. L. T., and Whitmore, G. A. (2010). Proportional hazards and threshold regression: their theoretical and practical connections. {\it Lifetime Data Analysis}, {\bf 16(2)}, 196-214.

\bibitem{Liestol94}
Liestol, K., Andersen, P.K., and Andersen, U. (1994).  Survival analysis and neural nets. {\it Statistics in Medicine}, {\bf 13(12)}, 1189-1200.

\bibitem{Longini89}
Longini, I.M., Clark, W.S., Byers, R.H., Ward, J.W., Darrow, W.W., Lemp, G.F., and Hethcote, H.W. (1989). statistical-analysis of the stages of HIV infection using a markov model. {\it Statistics in Medicine}, {\bf 8(7)}, 831-843.

\bibitem{Melendez12}
Melendez, R.G., Perez, M.O., Lopez, O.C., Kuri, A.J., and Espinola, Z.N. (2012). Effect of the treatment with allopurinol on the endothelial function in patients with hyperuricemia. {\it Endocrine Research}, {\bf 37(1)}, 1-6.

\bibitem{Moreno83}
Moreno, N.L., and Chiang, C.L. (1983). The life table and its applications. {\it Biometrics}, {\bf 41(1)}, 1-346.

\bibitem{Nakagawa06}
Nakagawa, T., Hu, H., Zharikov, S., Tuttle, K.R., Short, R.A., et al. (2006). A causal role for uric acid in fructose-induced metabolic syndrome. {\it American Journal of Physiology. Renal Physiology}, {\bf 290(3)}, 625-631.

\bibitem{DOQI02}
National Kidney Foundation. (2002). K/DOQI clinical practice guidelines for chronic kidney disease: evaluation, classification, and stratification. {\it Am J Kidney Dis},{\bf 39(2)}, 1-266.

\bibitem{Perperoglou13}
Perperoglou A. (2013). Cox models with dynamic ridge penalties on time varying effects of the covariates. {\it Statistics in Medicine}, {\bf 33(1)}, 170-180.

\bibitem{Ranganath16}
Ranganath, R., Perotte, A., et al. (2016). Deep survival analysis. {\it Proceedings of Machine Learning for Healthcare}, {\bf 56(1)}, 1-13. 

\bibitem{Sargent01}
Sargent, D.J. (2001). Comparison of artificial neural networks with other statistical approaches - Results from medical data sets. {\it Cancer}, {\bf 91(8)}, 1636-1642.

\bibitem{Suchting19}
Suchting, R., Hebert, E.T., Ma, P., Kendzor, D.E., and Businelle, M.S. (2019). Using Elastic Net Penalized Cox Proportional Hazards Regression to Identify Predictors of Imminent Smoking Lapse. {\it Nicotine  Tobacco Research : Official Journal of the Society for Research on Nicotine and Tobacco}, {\bf 21(2)}, 173-179.

\bibitem{Tibshirani97}
Tibshirani R. (1997). The lasso method for variable selection in the cox model. {\it Statistics in Medicine}, {\bf 16(4)},385-395.

\bibitem{Xiang00}
Xiang, A., Lapuerta, P., Ryutov, A., Buckley, J., and Azen, S. (2000). Comparison of the performance of neural network methods and Cox regression for censored survival data. {\it Computational Statistics Data Analysis}, {\bf 34(2)}, 243-257.

\bibitem{Yousefi17}
Yousefi, S., Amrollahi, F., Amgad, M., Dong, C., Lewis, J.E., Song, C., et al. (2017). Predicting clinical outcomes from large scale cancer genomic profiles with deep survival models. {\it Scientific Reports}, {\bf 7(1)}, 1-11.

\bibitem{Yu11}
Yu, C.N., Greiner, R., Lin, H.C., and Baracos, V. (2011). Learning patient-specific cancer survival distributions as a sequence of dependent regressors.  {\it Proceedings of the 24th International Conference on Neural Information Processing Systems}, {\bf 2011}, 1845-1853. 

\bibitem{Zhang08} 
Zhang, L., Zhang, P., Wang, F., Zuo, L., Zhou, Y., Shi, Y., Li, G., Jiao, S., Liu, Z., Liang, W., and Wang, H. (2008). Prevalence and factors associated with CKD: a population study from Beijing. {\it American Journal of Kidney Diseases : the Official Journal of the National Kidney Foundation}, {\bf 51(3)}, 373-384.

\bibitem{Zhu16}
Zhu, X., Yao, J., and Huang, J. (2016). Deep convolutional neural network for survival analysis with pathological images. {\it IEEE International Conference on Bioinformatics and Biomedicine}. {\bf 2016}, 544-547.

\bibitem{Vincent96}
Vincent, J.L., Moreno, R., Takala, J., Willatts, S., et al. (1996). The SOFA (Sepsis-related Organ Failure Assessment) score to describe organ dysfunction/failure.  {\it Intensive Care Medicine}, {\bf 22(7)}, 707-710.




























\end{thebibliography}