%\newpage                                    %
%\thispagestyle{plain}                       %
%\addcontentsline{toc}{chapter}{ABSTRACT}
\begin{center}
{\zihao{2}\enbiaoti}
\vspace{1cm}

%{\zihao{3}

\begin{tabular}{c}
  \englishname \\
  % Major:      & \researcharea   \\
  Directed by \advisor \\
\end{tabular}
%}
\vspace{1.5cm}

{\huge\bf ABSTRACT}
\end{center}
\vspace{.6cm}

% ÇëÌîÈëÓ¢ÎÄÕªÒª£º


It is a significant research work to accurately predict the mortality of patients with severe 
renal failure. It can make early assessment of patients' disease and preliminary prediction 
of clinical outcomes, allowing clinicians to carry out early intervention in severe patients 
according to the expected outcome and reasonable care for patients to avoid their disease 
progression. In addition, it also plays an important role in reducing the risk of death 
and allocating medical resources reasonably. Survival analysis is a statistical method 
that studies the timing of events, including death, disease recurrence, customer loss, 
and so on. It has a wide range of applications in biomedical, engineering, and finance. 
At present, many survival analysis models have been developed, but the comparison of these 
survival analysis models in the data of patients with severe renal failure has not been 
well applied. At present, the evaluation method of survival analysis results is relatively 
simple, and few studies have carried out comprehensive evaluation.



In view of the above problems, this paper has carried on the in-depth research. Firstly, 
by comprehensively considering missing values and outliers in the data of patients with 
severe renal failure, different processing methods were used for variables of different 
types, different missing rates and different importance, so as to reduce the influence of 
data quality on experimental results. Then, six survival statistical models, including 
Cox-ElasticNet, RSF, DeepSurv, Cox-CC, Cox-Time and LogisitcHazard, were applied to the 
clinical data of patients with severe renal failure to predict and analyze the mortality of 
patients. Different survival analysis statistical models were compared and evaluated in all 
aspects by C index, $C^{td}$, BS, IBS and ROC-Time. For the proportional risk 
model, this paper uses consistency index to evaluate the differentiation of the model, and 
for the non-proportional risk model, this paper uses $C^{td}$index to evaluate. ROC-Time was 
used to evaluate the prediction accuracy and stability of the model, and BS and IBS were used 
to evaluate the calibration degree of the model. Finally, the main risk factors and protective 
factors of renal failure patients were discussed.

The results of this paper show that for the six models studied, the model with the best prediction 
distinction is Cox-CC model, followed by Cox-Time model. The model with the best prediction accuracy 
is Cox-ElasticNet model, and the model with the best stability is Cox-CC model. The RSF model performs 
best in terms of the calibration degree of the model, and the Cox-CC model performs best in terms of 
the long-term prediction accuracy and stability, while the RSF model performs best in terms of the 
medium and short term prediction accuracy. Finally, the Cox-ElasticNet model was used to calculate 
the risk factors and protective factors of patients with severe renal failure. The most important risk 
factors were: minimum blood urea nitrogen within 24 hours after admission to ICU; The most important 
protective factor was the minimum oxygenation index within 24 hours of admission to the ICU. The establishment 
of such an optimal survival analysis statistical model is expected to provide necessary reference for 
clinical medical staff to develop a more scientific and reasonable prognostic diagnosis method, so as 
to play a positive impact on the rehabilitation of patients with severe renal failure.

\vspace{0.2cm}

\noindent{\zihao{-4}{\bf Key words:} Deep learning;\; Renal failure;\; ICU}
